The Astropy Project

### 2017-10-29 main.tex
2.3

\subsection{Astropy development model, astropy ecosystem}
\inlinecomment{Needs writing by EJT}

This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.

>>>>

\subsection{Astropy development model}
\inlinecomment{Adrian started this, but needs some filling in by EJT}

Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution}, \url{http://docs.
astropy.org/en/stable/development/workflow/development_workflow.html}}

As of version XX, \astropypkg contains XX lines of code contributed by XX unique
contributors over XX \texttt{git} commits.
The majority of the commits were and are contributed by a subset of the
contributor pool: XX percent of the commits were contributed by XX contributors.
